Towards a Mechanized Proof of Noninterference

### 2013-12-18 paper/paper.tex

\documentclass[a4paper]{article}
\usepackage{mathpartir}
\usepackage{amssymb}
%\usepackage{float}
%\floatstyle{boxed}
%\restylefloat{figure}

\newcommand{\langName}[0]{TinyML\textsuperscript{2}}
\newcommand{\typeRule}[3]
{#1 \textsf{ } \vdash \textsf{ } #2 \textsf{ } \colon \textsf{ } #3}
\newcommand{\guards}[0]{\lhd}

@@

Citing something for now to make an error message go away~\cite{Pierce:SF}.
Abstract goes here, summarize what this paper covers and what we ended up with.

@@

\begin{figure}
  \begin{mathpar}
    \infer[S-Int]
    {
    l \leq l'
    }
    {
    \textsf{int}^l \leq \textsf{int}^{l'}
    }

@@

\begin{figure}
  \begin{mathpar}
    \infer[G-Int]
    {
    l \leq l'
    }
    {
    l \guards \textsf{int}^{l'}
    }

@@

\begin{figure}
  \begin{mathpar}
    \infer[V-Int]
    { }
    {\typeRule{\Gamma}{k}{\textsf{int}^{*}}}

@@

\begin{figure}
  \begin{mathpar}
    \infer[E-Value]
    {
    \typeRule{\Gamma}{v}{t}
    }
    {
    \typeRule{*, \Gamma}{v}{t}
    }

@@

The type system for our simple language is given in Figure~\ref{fig:value_types}.

@@

I'm imagining this section could outline the human version of the proofs we'd
need to do a full noninterference proof.

>>>>

\documentclass[a4paper]{article}
\usepackage{mathpartir}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{float}
%\floatstyle{boxed}
%\restylefloat{figure}

\newcommand{\langName}[0]{TinyML\textsuperscript{2}}
\newcommand{\origLang}[0]{CoreML\textsuperscript{2}}
\newcommand{\typeRule}[3]{#1 \vdash #2 \colon #3}
\newcommand{\guards}[0]{\lhd}
\newcommand{\lift}[1]{\lfloor #1 \rfloor}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

@@

Abstract goes here, summarize what this paper covers and what we ended up with.

@@

\begin{figure}[h!]
  \begin{mathpar}
    \infer[S-Int]
    {
    l \leq l'
    }
    {
    \textsf{int}^l \leq \textsf{int}^{l'}
    }

@@

\begin{figure}[h!]
  \begin{mathpar}
    \infer[G-Int]
    {
    l \leq l'
    }
    {
    l \guards \textsf{int}^{l'}
    }

@@

Figure~\ref{fig:value_types} includes typing judgements for values and
Figure~\ref{fig:expr_types} includes typing judgements for expressions.

\begin{figure}[h!]
  \begin{mathpar}
    \infer[V-Int]
    { }
    {\typeRule{\Gamma}{k}{\textsf{int}^{*}}}

@@

\begin{figure}[h!]
  \begin{mathpar}
    \infer[E-Value]
    {
    \typeRule{\Gamma}{v}{t}
    }
    {
    \typeRule{*, \Gamma}{v}{t}
    }

@@

@@

Before discussing the task of mechanizing a noninterference theorem for
\langName, it is useful to first view what the natural language proof would
look like first.  We first start by proving some supporting lemmas and finish
with a proof of noninterference for the language.  Since \langName is a stripped
down version of \origLang, the proof will look like a simplified version of the
proof found in Pottier and Simonet's paper~\cite{InfoFlowML}.

234101415

\begin{lemma}[Soundness]
  \label{lem:soundness}
  Let $i \in \{1, 2\}$. If $e \to e'$, then $\lift{e}_i \to \lift{e'}_i$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}
  \label{lem:stuck_bracket}
  If $e$ is stuck, then $\lift{e}_i$is stuck for some $i \in \{1, 2\}$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}[Completeness]
  \label{lem:stuck_bracket}
  If $e$ is stuck, then $\lift{e}_i$is stuck for some $i \in \{1, 2\}$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}[Substitution]
  \label{lem:stuck_bracket}
  Assume $\typeRule{ }{v}{s}$.  Then, $\typeRule{\Gamma[x \mapsto s]}{v'}{t}$
  implies $\typeRule{\Gamma}{v'[x \Leftarrow v]}{t}$.  Also $\typeRule{pc,
  \Gamma[x \mapsto s]}{e}{t}$ implies $\typeRule{pc, \Gamma}{e[x \Leftarrow
  v]}{t}$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}
  Let $H$ be an upward-closed subset of the label lattice $\mathcal{L}$.  Let $l
  \not\in H$.  If, using $H$ for the set of high labels, $\typeRule{
  }{e}{\textsf{int}^l}$ and $e \to^* v$ then $\lift{v}_1 = \lift{v}_2$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{thm}[Noninterference]
  Choose $l, h \in \mathcal{L}$ such that $h \not\leq l$.  Let $h \guards t$.
  Assume $\typeRule{(x \mapsto t)}{e}{\textsf{int}^l}$, where $e$is a \langName
  expression.  If, for all $i \in \{1, 2\}$, $\typeRule{ }{v_i}{t}$ and $e[x
  \Leftarrow v_i] \to^* v_i'$ hold, then $v_1' = v_2'$.
\end{thm}
\begin{proof}
  TODO
\end{proof}
